skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-07-13 paper/paper.tex
recompiled

\author[FirstAuthorLastName \textit{et~al}.]{
Stephen D. Turner\,\textsuperscript{1},
V.P. Nagraj\,\textsuperscript{1},
Matthew Scholz\,\textsuperscript{1},
Shakeel Jessa\,\textsuperscript{1},
Carlos Acevedo\,\textsuperscript{1},
Jianye Ge\,\textsuperscript{2},
August Woener\,\textsuperscript{2},
Bruce Budowle\,\textsuperscript{2},
}

>>>>

\author[FirstAuthorLastName \textit{et~al}.]{
Stephen D. Turner\,\textsuperscript{1}, V.P.
Nagraj\,\textsuperscript{1}, Matthew
Scholz\,\textsuperscript{1}, Shakeel Jessa\,\textsuperscript{1}, Carlos
Acevedo\,\textsuperscript{1}, Jianye Ge\,\textsuperscript{2}, August
Woener\,\textsuperscript{2}, Bruce Budowle\,\textsuperscript{2}
}
